Title

### 2014-01-14 paper/paper.tex
Added some text to the paper.
Added my attempt at the abstract.
Added sections on aggregate statistics for the different community-types.
Modify Elisa's abstract.
Added References Final Title and Added Abstract

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Input Your Paper Title Here)
/Author (John Doe, Jane Doe)
/Keywords (Input your paper keywords in this optional area)}

@@

% Title, Author, and Address Information
\title{
%Followers are not enough: Beyond structure in the detection of communities \\
Followers are not enough: Exploring the communities that exist beyond structure \\
%Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
%Followers are not enough: Beyond structural communities in online social networks
% \\
 %Followers are not enough: exploring communities beyond structure
 }
%   \author{David Darmon  \\
%  University of Maryland\\
% Dept. of Mathematics \\
% ddarmon@math.umd.edu \\
%  \And Elisa Omodei \\
%  LaTTiCe (CNRS, ENS, Paris 3)\\
% ISC-PIF\\
% elisa.omodei@ens.fr \\
%  \And 
%  Joshua Garland\\
%  University of Colorado at Boulder\\
% Dept. of Computer Science \\
% joshua.garland@colorado.edu}

@@

\begin{abstract}
\begin{quote}
[[Joshua]]

[[David]]

[[Elisa]]

\end{quote}
\end{abstract}

\input{parts/intro.tex}
\input{parts/community.tex}
\input{parts/methods.tex}
\input{parts/results.tex}
\input{parts/discussion.tex}
\input{parts/conclusion.tex}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\usepackage{multirow}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Input Your Paper Title Here)
/Author (David Darmon, Elisa Omodei, Joshua Garland)
/Keywords (Input your paper keywords in this optional area)}

@@

% Title, Author, and Address Information
\title{
%Followers are not enough: Beyond structure in the detection of communities \\
Followers are Not Enough: Beyond Structural Communities in Online Social Networks%\\
%Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
%Followers are not enough: exploring communities beyond structure
 }

% \author{David Darmon  \\
% University of Maryland\\
% Dept. of Mathematics \\
% ddarmon@math.umd.edu \\
% \And Elisa Omodei \\
% LaTTiCe (CNRS, ENS, Paris 3)\\
% ISC-PIF\\
% elisa.omodei@ens.fr \\
% \And 
% Joshua Garland\\
% University of Colorado at Boulder\\
% Dept. of Computer Science \\
% joshua.garland@colorado.edu}

@@

\begin{abstract}
\begin{quote}
Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter. But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with. We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network. The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups. In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based. We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings. We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network. Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights into the network under study.
\end{quote}
\end{abstract}

\input{parts/intro.tex}
\input{parts/community.tex}
\input{parts/methods.tex}
\input{parts/results.tex}
\input{parts/discussion.tex}
\input{parts/conclusions.tex}

### 2014-01-14 paper/parts/methods.tex
Added References Final Title and Added Abstract

In network theory communities are usually defined as group of nodes more densely connected among each other than with the rest of the network. Community detection is a well studied but not yet solved problem, and several different methods and algorithms have been proposed. For a complete review of the subject we refer the reader to (\textbf{ref: Fortunato, Santo. "Community detection in graphs." Physics Reports 486.3 (2010): 75-174.}). In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people). Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities (\textbf{ref: J. Baumes, M.K. Goldberg, M.S. Krishnamoorthy, M.M. Ismail, N. Preston, Finding communities by clustering a graph into overlapping subgraphs, in: N. Guimaraes, P.T. Isaias (Eds.), IADIS AC, IADIS, 2005, pp. 97–104; Palla, Gergely, et al.
 "Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.; S. Zhang, R.-S. Wang, X.-S. Zhang, Identification of overlapping community structure in complex networks using fuzzy c-means clustering, Physica A 374 (2007) 483–490; Gregory S (2007) An algorithm to find overlapping community structure in networks. In: Proceedings of the 11th European Conference on Principles and Practice of Knowledge Discovery in Databases (PKDD 2007).
Berlin, Germany: Springer-Verlag. pp 91–102.; T. Nepusz, A. Petroczi, L. Negyessy, F. Bazso, Fuzzy communities and the concept of bridgeness in complex networks, Phys. Rev. E 77 (1) (2008) 016107; 
Lancichinetti A, Fortunato S, Kertesz J (2009) Detecting the overlapping and hierarchical community structure in complex networks. New J Phys 11: 033015.; 
vans TS, Lambiotte R (2009) Line graphs, link partitions, and overlapping communities. Phys Rev E 80: 016105. 25; Kovacs, Istvan A., et al. (2010) 
Community landscapes: An integrative approach to determine overlapping network module hierarchy, identify key nodes and predict network dynamics. PloS ONE 5: e12528}). 
Among these, even fewer can also deal with directed or weighted networks. Palla et al. clique percolation method can for example take into account these two features, but not both at the same time (\textbf{ref: Palla, Gergely, et al. "Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.}). Lancichinetti et. al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) (\textbf{ref: Lancichinetti, A., Radicchi, F., Ramasco, J. J., and Fortunato, S. (2011). Finding statistically significant communities in networks. PloS one, 6(4), e18961.}). Their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}), and it allowed us to detect overlapping communities on our weighted directed networks.

>>>>

In network theory communities are usually defined as group of nodes more densely connected among each other than with the rest of the network. Community detection is a well studied but not yet solved problem, and several different methods and algorithms have been proposed. For a complete review of the subject we refer the reader to \cite{fortunato2010community}. In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people). Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010} Among these, even fewer can also deal with directed or weighted networks. Palla et al. clique percolation method can for example take into account these two features, but not both at the same time \cite{PalEtAl05}. Lancichinetti et. al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) \cite{LancichinettiPlos}. Their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}), and it allowed us to detect overlapping communities on our weighted directed networks.
